An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-14 VLDB2026/main.tex
Update main.tex

>>>>

	Most algorithms exhibit the worst performance on the OOD dataset text2image. However, ACORN, UNG, and FilteredVamana show relatively stable performance on text2image. Their performance drops less compared to in-distribution (ID) datasets such as GIST and GLOVE, indicating better adaptability to OOD queries.
